Output Summary

### 2023-05-04 03-post-process/output-plots-children/06-length-based-survival.Rmd
Clean up misc typos

  # predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
              yrs = all_yrs[t])

@@

  plot(1,1, type = "n", 
       ylim = phi_Pa_Mb_lim,
       xlim = range(L_Pb_seq), 
       main = pops[j]
  )

>>>>

  # predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
              yrs = all_yrs[ts_yrs])

@@

  plot(1,1, type = "n", 
       ylim = phi_Pa_Mb_lim,
       xlim = range(L_Pb_seq)
  )
  panel_label(pops[j])
